Predictive analytics in quality assurance for assembly processes: lessons learned from a case study at an industry 4.0 demonstration cell

### 2020-12-11 02_Paper/paper.tex
remove random forests.

To study which implementation would be more suitable for industrial applications, we compare Multilinear Perceptrons (MLPs), Support Vector Machines (SVM), as well as random forests on the task of quality prediction. All three will be introduced next.

@@

We compare a total of three different classifier architectures on the data.
A Support Vector Machine (SVM), a Multilayer Perceptron (MLP) and a Random Forest
structure. All three methods are trained using standard hyperparameters.
\footnote{To allow exact reproduction of these results source
code is available at \url{https://github.com/manubrain/Demo-Cell-Classification}}

\begin{table}
       \centering
       \begin{tabular}{ c c } \toprule
              Approach         & accuracy \\ \midrule
              Na\"ive-Baseline & 64 \% \\
              Support Vector Machine & 82 \% \\
              Multilayer Perceptron & 88 \% \\
              Decision Tree         & 98 \% \\ \bottomrule
       \end{tabular}
       \caption{Comparison of Support Vector Machine (SVM), Multilayer Perceptron and 
                Random Forest classification on our anomaly detection task. 
                The first row shows the performance of naively predicting a broken piece
                every time.}
       \label{tab:class_comp}
\end{table}

\AP{According to Prof. Garcke, we should stick either with "Random Forest" or with "Decision Tree". I would like you, Moritz, to decide what would be the best for this case.}

@@

The outcome of the models shows that the random forest performed best followed by the multilayer perceptron and the support vector machine. However, by reviewing the confusion matrices presented in Table~\ref{tab:Confusion_matrix}, multilayer perceptron would be the preferred solution to be implemented in industrial applications due to the 0\% ratio in false-positive results and high accuracy of 88\%.

>>>>

To study which implementation would be more suitable for industrial applications, we compare Multilayer Perceptrons (MLPs), Support Vector Machines (SVM), as well as decision trees on the task of quality prediction. All three will be introduced next.

@@

We compare a total of three different classifier architectures on the data.
A Support Vector Machine (SVM), a Multilayer Perceptron (MLP) and a Decision Tree
structure. All three methods are trained using standard hyperparameters.
\footnote{To allow exact reproduction of these results source
code is available at \url{https://github.com/manubrain/Demo-Cell-Classification}}

\begin{table}
       \centering
       \begin{tabular}{ c c } \toprule
              Approach         & accuracy \\ \midrule
              Na\"ive-Baseline & 64 \% \\
              Support Vector Machine & 82 \% \\
              Multilayer Perceptron & 88 \% \\
              Decision Tree         & 98 \% \\ \bottomrule
       \end{tabular}
       \caption{Comparison of Support Vector Machine (SVM), Multilayer Perceptron and 
                Decision Tree classification on our anomaly detection task. 
                The first row shows the performance of naively predicting a broken piece
                every time.}
       \label{tab:class_comp}
\end{table}

@@

The outcome of the models shows that the decision tree performed best followed by the multilayer perceptron and the support vector machine. However, by reviewing the confusion matrices presented in Table~\ref{tab:Confusion_matrix}, multilayer perceptron would be the preferred solution to be implemented in industrial applications due to the 0\% ratio in false-positive results and high accuracy of 88\%.
